Make any stupid plot you want

### 2021-01-26 draft/sections/math.tex
rewrote nus

\subsubsection{Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a simple 2D opaque image $D=\mathbb{R}^5$ with an element $d \in D$ of the form
\begin{equation}
    d = (x, y, r, g, b)
\end{equation}
such that a graphic only has 2D position and color. To support overplotting and transparency, the fiber would be $D=R^{7}$ such that $d=(x, y, z, r, g, b, a)$. The location coordinates $x$ and $y$ are defined in terms of the display, while the $(r,g,b)$ values are filled in via a lookup on $S$.

@@

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels,} in fiber $P$. The visual transformer $\nu$ is a set of functions each targeting a different $\mu$
\begin{equation}
    \label{eq:nu_expanded}
    \{\nu_{0}, \ldots, \nu_{n}\}: \{\tau_{0}, \ldots, \tau_{n}\} \mapsto \{\mu_{0}, \ldots, \mu_{n}\}
\end{equation}

where $\mu_{i}$ are the visual parameters in the assembly function $Q(\mu_{0}, \ldots, \mu_{n})(s) = \rho(s)$.

\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/artist_stages.png}
    \caption{The artist $A$ converts data into the visual variables in $V$ and then composes those visual variables into a graphic in $H$}
    \label{fig:artist_stages}
\end{figure}
\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \label{tab:mpl_visual_variable_fiber}
\end{table}

@@

\subsubsection{Visual Channels}
\label{sec:artist_nu}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/equivariance_nu.png}
    \caption{An equivariant $\nu$ preserves monoid actions. Here $\nu$ maps the words to the emojis and is constructed such that a permutation of the words is reflected in a permutation of the symbols. \note{will switch to a figure table thing but this is the idea}}
    \label{fig:artist_nu}
\end{figure}
The expectation of a visual transformation is that it will convert data to visual variables in a consistent manner. For example in figure~\ref{fig:artist_nu}, the $\nu$ maps words to emojies. Our constraint on $\nu$ is that if we shuffle the words, the emojis should be shuffled such that the map defined by $\nu$ is still valid. We construct $\nu: E \rightarrow V$ as an equivariant map such that there is a homomorphism from left monoid actions on $E_{i}$ to left monoid actions on $V_{i}$ where $i$ identifies a field in the fiber. $E_i$ and $V_{i}$ each contain a set of values as defined in $F$ and $P$ respectively. A validly constructed $\nu$ is one where the  diagram 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "m_e"'] & V_i \arrow[d, "m_v"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
commutes such that $\nu_i(m_e(E_i)) = m_v(\nu_i(E_i))$.

\paragraph{Example: Ordering}
To preserve ordering of elements, $\nu$ must be a monotonic function such that given $e_1, e_2 \in E_{i}$
\begin{equation}
\text{ if } e_1 \leq e_2 \text{ then } \nu(e_1) \leq \nu(e_2)
\end{equation}

\paragraph{Example: Translation}
A $\nu$ is equivariant under translation monoid actions if 
\begin{equation}
\nu(x + c) = \nu(x) + \nu(c)
\end{equation}

\paragraph{Example: Invalid $\nu$}
Given a transform $t(x) = x+2$, we construct a $\nu$ that always takes data to .5: 
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "2e"'] & V_i \arrow[d, "2v"] \\
        E_1 \arrow[r, "\lambda"]                                        & V_1                 
    \end{tikzcd}
\end{equation}

This $\nu$ is invalid because the graph does not commute for $t$:
\begin{align}
    \nu(t(e)) & \overset{?}{=} t(\nu(e))\\
    .5 & \overset{?}{=} t(.5)\\
    .5 & \neq 2*.5
\end{align}

To construct a valid $\nu$, the diagram must commute for all monoid actions on the sets in $E_i, V_i$.

>>>>

\subsubsection{Abstract Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a 2D opaque image $D=\mathbb{R}^5$ with elements in $D$ of the form
\begin{equation}
    d = (x, y, r, g, b)
\end{equation}
such that a rendered graphic only consists of 2D position and color. To support overplotting and transparency, the fiber could be $D=R^{7}$ such that $d=(x, y, z, r, g, b, a)$. The location coordinates $x$ and $y$ are defined in terms of the display, while the $(r,g,b)$ values are filled in via a lookup on $S$.

@@

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels,} in fiber $P$.
\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/artist_stages.png}
    \caption{The artist $A$ converts data into the visual variables in $V$ and then composes those visual variables into a graphic in $H$}
    \label{fig:artist_stages}
\end{figure}
\subsubsection {Visual Fiber Bundle}

For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|L|l|}\hline
     $\bm{\nu_{i}}$                      & $\bm{\mu_{i}}$                                                            & $\bm{codomain(\nu_{i})}$  \\ \hline                                              
    position                    & x, y, z, theta, r                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}^{+}$   \\ \hline
    shape                       & markerstyle                                                      & $\{f_{0}, \ldots, f_{n}\}$ \\ \hline
    color                       & color, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^{4}$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $\mathbb{N}^{10}$\\\cline{2-3}
                                & linestyle                                                        & $\{f_{0}, \ldots, f_{n}\} \times (\mathbb{R}, \mathbb{R^+}^{n, n\%2=0})$ \\ \hline              
    \end{tabulary}
    \label{tab:mpl_visual_variable_fiber}
\end{table}

@@

\subsubsection{Visual Channels}
\label{sec:artist_nu}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/equivariance_nu.png}
    \caption{An equivariant $\nu$ preserves monoid actions. Here $\nu$ maps the words to the emojis and is constructed such that a permutation of the words is reflected in a permutation of the symbols. \note{will switch to a figure table thing but this is the idea}}
    \label{fig:artist_nu}
\end{figure}
As introduced in section~\ref{sec:intro_visual_variables}, there are many ways to encode data visually. We define the visual transformers $\nu$ as the set of conversion functions 
\begin{equation}
    \label{eq:nu_expanded}
    \{\nu_{0}, \ldots, \nu_{n}\}: \{\tau_{0}, \ldots, \tau_{n}\} \mapsto \{\mu_{0}, \ldots, \mu_{n}\}
\end{equation}
such that $\nu_i: \tau_i \mapsto \mu_i$ is an equivariant map such that there is a monoid homomorphism from $F_{i}$ to $V_{i}$. A validly constructed $\nu$ is one where the  diagram 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "m_e"'] & V_i \arrow[d, "m_v"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
commutes such that $\nu_i(m_e(E_i)) = m_v(\nu_i(E_i))$. This equivariance constraint yields guidance on what makes for an invalid transform. For example, the single value conversion $\nu_{i}(x) = .5$ does not commute under translation  $t(x) = x+2$  
\begin{align}
    \nu(t(e + 2)) & \overset{?}{=} \nu(e) + \nu(2)\\
    .5 &\neq .5 + .5
\end{align}

On the other hand figure~\ref{fig:artist_nu} illustrates a valid $\nu$ mapping from \textbf{Strings} to symbols. The group action on these sets is permutation, so shuffling the words must have an equivalent shuffle of the symbols they are mapped to. To preserve ordinal and partial order monoid actions, $\nu$ must be a monotonic function such that given $e_1, e_2 \in E_{i}$, $\text{ if } e_1 \leq e_2 \text{ then } \nu(e_1) \leq \nu(e_2)$. For interval scale data, $\nu$ is equivariant under translation monoid actions if $\nu(x + c) = \nu(x) + \nu(c)$. For ratio data, there must be equivalent scaling $ \nu(xc) = \nu(x)\nu(c)$.
